The symmetry problem of the \textit{Fermi} and eROSITA bubbles: A proof-of-concept study

### 2022-02-04 paper.tex
update

Early attempts \citep{Sarkar2015,Yang2017,Zhang2020}\
to model the symmetric Fermi and eROSITA bubbles (collectively we call the Galactic bubbles)\
assumed that the jet is vertical to the Galactic plane. However,\
observation \citep{Gallimore2006} has proposed that\
there is a lack of preferred orientation of jets with respect to the plane of the disc.\
A number of galaxies in which the jets are tilted to the disc normal\
(e.g. NGC 3079, \citealt{Cecil2001}; NGC 1052, \citealt{Dopita2015}),\
including galaxies in which the jets lie in the plane of the disc (e.g. IC 5063, \citealt{Morganti2015}).

To this end, this work introduces a dense thin disk of interstellar medium\
around a jet source to deflects and decelerates the jets,\
in an attempt to remedy the symmetry problem of the Galactic bubbles.\

@@

  Since the relativistic fluid ejected by the jet source\
  is quickly stalled off and slowed down by a dense ISM disk in a short time,\
  and the relativistic fluid\
  accounts for a little minority of total mass inside the simulation box,\
  we still use the Newtonian gravity to attack this problem.

@@

  With the help of the isothermal and hydrostatic equilibrium conditions,\
  and assuming the interfaces between isothermal disk and atmosphere are in thermal pressure equilibrium,\
  we can write the steady-state gaseous density distributions,\
  confined in the total potential, of the disk and the Galactic atmosphere as\
  \begin{subequations}
  \begin{align}
     \displaystyle \rho_{\text{isoDisk}}(z) = \rho_{\text{isoDisk}}^{\text{peak}}
     \exp\left[-\frac{\Phi_{\text{total}}(z)}{k_{B}T_{\text{isoDisk}}/m_{\text{p}}}\right]&\label{isothermal-disk-density}\\
     \text{, if $|z| < z_{0}$}& \nonumber \\
     \nonumber\\
     \displaystyle \rho_{\text{atmp}}(z) = \rho_{\text{atmp}}^{\text{peak}}
     \exp\left[-\frac{\Phi_{\text{total}}(z)}{k_{B}T_{\text{atmp}}/m_{\text{p}}}\right]&\label{isothermal-atmp-density}\\
     \text{, otherwise,}& \nonumber
  \end{align}
  \label{disk-atm-sys}
  \end{subequations}
  where $m_{\text{p}}$ is the proton mass,\
  $T_{\text{isoDisk}}$ and $T_{\text{atmp}}$ is the temperature of the isothermal disk and atmosphere,\
  $\rho_{\text{isoDisk}}^{\text{peak}}$ and $\rho_{\text{atmp}}^{\text{peak}}$ is the peak mass density\
  of the disk and atmosphere on the mid-plane $z=0$.

  We tabulate parameters in the first four\
  categories of \Cref{table-parameters},\
  except for $\rho_{\text{atmp}}^{\text{peak}}$ that\
  can be derived from the other known parameters and thermal pressure equilibrium condition\
  on the interfaces $(z=\pm z_{0})$ between the disk and atmosphere.\

  The density profile of \Cref{disk-atm-sys} is shown in \Cref{fig__initial-density-profile}.\
  Beyond the core radius ($\sim 2 \text{ kpc}$) the gaseous density decreases rapidly as a power-law.

%  The density profile of \Cref{disk-atm-sys} is shown in \Cref{fig__initial-density-profile}\
%  and compared to the observed result \citep{Miller_2013} beyond 1 kpc.\
%
%  Note that there is an difficulty in disentangling the contribution\
%  of the Local Bubble, a supernova remnant in which the Solar System is embedded \citep{Snowden1990},\
%  and the contribution from solar wind charge-exchange processes, which produce soft\
%  X-ray emission throughout the Solar System. As a result, the density profile of the Galactic halo remains unclear\
%  \citep{BlandHawthorn2016}.

  \begin{figure}
    \includegraphics[width=\columnwidth]{figures/fig__initial-density-profile.png}
    \caption{The density profile of the isothermal disk (red pluses) and\
             atmosphere (blue crosses) along the positive z-axis.\
             The density distribution is derived from hydrostatic equilibrium,\
             the interface ($z=0.1$) between the isothermal disk\
             and the atmosphere is pressure balanced.}
    \label{fig__initial-density-profile}
  \end{figure}

@@

  A crucial component in our work is the clumpy ISM disk initialized by\
  the publicly available pyFC code
  \footnote{\url{https://pypi.python.org/pypi/pyFC}}.\

  pyFC randomly generates dimensionless 3D scalar field $f(\bold{x})$\ % that is clumpy and porous.
  that obeys the log-normal probability distribution\
  with mean $\mu$ and dispersion $\sigma$,\
  and follows the power-law Kolmogorov spectrum
  \begin{equation}
    D(\bold{k})=\int k^{2} \hat{f}(\bold{k})\hat{f}^{*}(\bold{k})d\Omega \propto k^{-\beta},
    \label{Kolmogorov-spectrum}
  \end{equation}
  where $\hat{f}(\bold{k})$ is the Fourier transform of $f(\bold{x})$.\
  The spectrum $D(\bold{k})$ in the Fourier space is characterized by the power law index $\beta=5/3$,\
  the Nyquist limit $k_{\text{max}}$, and the lower cutoff wave number $k_{\text{min}}$.
  $k_{\text{max}}$ is one-half of the spatial resolution within disk,\
  and $k_{\text{min}}$ is 375.0, corresponding to the maximum size of an individual clump $\sim 20$ pc.\
  \citet{LA2002} and \citet{Wagner2012} have outlined a detailed procedure\
  for constructing a clumpy scalar field, and we do not repeat here.

  The density of clumpy disk can thus be obtained by taking the scalar products of\
  $f(\bold{x})$ with $\rho_{\text{isoDisk}}(z)$ over all cells within the disk, i.e.,\
  $\displaystyle\rho_{\text{ismDisk}}(\bold{x}) =\
  f(\bold{x}) \rho_{\text{isoDisk}}(z)$.\
  Also, the thermal pressure equilibrium within the clumpy disk implies that the temperature of disk is
  $\displaystyle T_{\text{ismDisk}}(\bold{x}) =\
  T_{\text{isoDisk}}(z)\rho_{\text{isoDisk}}(z)/\rho_{\text{ismDisk}}(\bold{x})$.

  \Cref{table-parameters} summarize the parameters of the clumpy disk and their references.

  On the basis of this setup, we cover the AMR base level with\
  $16\times16\times32$ root cells, refined progressively on the mid-plane $z=0$\
  based on the gradient of mass density.\
  We also restrict the refinement level at 7 within the cold disk so that\
  a molecular cloud can be adequately resolved by approximately 30 cells along their diameter, 20 pc.

  \Cref{fig__zoom-in-disk} shows a close-up view of the\
  pressure, temperature, and number density slices
  in the y-z plane through the center of the disk.

  \Cref{fig__numberDensityHistogram} plots the volume filling factor as a function of\
  initial number density within the disk without jet source.\

  \begin{figure}
      \includegraphics[width=\columnwidth]{figures/fig__numberDensityHistogram.png}
    \caption{The volume filling factor as a function of\
             initial number density within the disk without jet source.\
             The vertical bands represent from left to right: the allowable number densities \citep{peak-ism-density} for\
             hot ionized, warm neutral (WNM), warm ionized (WIM), cold nuetral mediums (CNM), and molecular clouds.}
      \label{fig__numberDensityHistogram}
  \end{figure}

  \begin{figure}
    \includegraphics[width=\columnwidth]{figures/fig__zoom-in-disk.png}
    \caption{Close-up view of the initial\
             pressure (top), temperature (middle), and number density (bottom) slices\
             in the y-z plane through the center of the disk.
             }
    \label{fig__zoom-in-disk}
  \end{figure}

\begin{table*}[t]
\raggedright
\caption{Parameters of the disk, atmosphere, and gravitational potential in the simulation.}
\label{table-parameters}
\begin{tabular}{@{}llrc@{}}
\toprule[1pt]\midrule[0.3pt]
Parameter                             & Description                               & Value                                &  Reference                     \\ \midrule
{\bf Static stellar potential }       &                                           &                                      &                                \\
$\sigma_{\text{bulge}}$               & Velocity dispersion of bulge              & 100 km$\cdot$s$^{-1}$                & \citep{velocity-dispersion-MW} \\
$\rho_{\text{bulge}}^{\text{peak}}$   & Peak average density of bulge             & $4\times 10^{-24}$ g$\cdot$cm$^{-3}$ &   N/A                          \\ \hline
{\bf Static dark halo potential }     &                                           &                                      &                                \\
$v_{\text{halo}}$                     &                                           & 131.5 km$\cdot$s$^{-1}$              & \citep{Johnston1995}           \\
$d_{\text{h}}$                        & Core radius                               & 12 kpc                               & \multicolumn{1}{c}{''}         \\ \hline
{\bf Atmosphere }                     &                                           &                                      &                                \\
$T_{\text{\text{atmp}}}$              & Temperature of atmosphere                 & $10^{6}$ K                           & \citep{temperature-MW}         \\ \hline
{\bf Isothermal disk }                &                                           &                                      &                                \\
$z_{0}$                               & Scale height of disk                      & 100 pc                               & \citep{peak-ism-density}       \\
$T_{\text{\text{isoDisk}}}$           & Temperature of disk                       & $10^{3}$ K                           & \multicolumn{1}{c}{''}         \\
$\rho_{\text{isoDisk}}^{\text{peak}}$ & Peak mass density of disk                 & $10^{-23}$ g$\cdot$cm$^{-3}$         & \multicolumn{1}{c}{''}         \\ \hline
{\bf Clumpy disk }                    &                                           &                                      &                                \\
$\dagger$  $k_{\text{min}}$           & Cutoff wave number                        & 375.0                                & \citep{peak-ism-density}       \\
$\mu$                                 & Mean of scalar field                      & 1.0                                  &   N/A                          \\
$\ddag$  $\sigma$                     & Dispersion of scalar field                & 5.0                                  & \citep{Federrath2010}          \\
$\beta$                               & Power law index                           & -5/3                                 &   N/A                          \\ \midrule
\end{tabular}
\begin{tablenotes}
      \raggedright
      \item  $\dagger$  $k_{\text{min}}=375.0$ leads to the size of an individual molecular cloud $\sim 100$ pc.
      \item  $\ddag$ In numerical simulations of turbulence,\
             \citet{Federrath2010} find $\sigma\sim 3.6$ and 35 for solenoidal (divergence-free)\
             and compressive (curl-free) driving force,\
             respectively, so that our adopted value of 5 is closer to their solenoidal result.
    \end{tablenotes}
\end{table*}

% In addition to the gravitational interaction, we ignore other interactions between stars and gases.
% We also ignore the self-gravity of the ISM disk and of the atmosphere.
% We ignore the centrifugal force of Milky Way rotation acting on the bubbles.
%

@@

  Motivated by these observations, we simulate the jet with an inclination angle\
  $45^{\circ}$ with respect to the Galactic plane\
  in order to release the caveat that\
  the jet direction must be perpendicular to the Galactic plane, and in particular to\
  investigate the effect of the jet-disk misalignment on the symmetry of bubbles.

@@

  Note that as we inject the jets at the center of the clumpy disk,\
  we define the ambient gas density by the peak density of\
  the isothermal disk on the mid-plane $z=0$ (i.e. $\rho^{\text{peak}}_{\text{isoDisk}}$),\
  as opposed to the \textit{clumpy} density around the jet source, to avoid ambiguous definition.

@@

\section{Results}
\label{Results}
  \begin{figure}
    \includegraphics[width=\columnwidth]{figures/fig__jetI5+ismSeed3-45deg_no-disk-stratified-ambient-Pres-Dens-Temp.png}
    \caption{
             The pressure (top), temperature (middle), and number density (bottom) slices\
             through a bipolar jet sources injecting along $z=-y$ direction from\
             the origin for a duration of 1.2 Myr under four different cases from left to right.\
             Comparison between the cases with a clumpy (first column from left)\
             and with a smooth disk (second) in a stratified atmosphere\
             shows that the initial density distribution of the dense disk has an insignificant effect\
             on the overall dynamics of bubbles. However, the outer bubbles with the smooth disk\
             in an uniform atmosphere (third) is spherical-shape,\
             suggesting the stratification facilitates the outer bubbles elongation significantly.\
             Also, the first three and the rightmost columns show that the most inner bubbles (dashed box)\
             can only appear associated with the disk, and without the disk, the outer bubbles will be tilted,
             indicating the dense disk is crucial for\
             the axis-symmetrically outer bubbles and of the most inner bubbles formation.
             }
    \label{fig__jetI5+ismSeed3-45deg_no-disk-stratified-ambient-Pres-Dens-Temp}
  \end{figure}

@@

  \begin{figure*}
    \subfigure[Simulated (top) and observed (bottom; \citealt{Predehl2020}) count rate\
               (photons s$^{-1}$ deg$^{-2}$) in the 0.6-1.0 keV range,\
               using a Hammer-Aitoff projection. Throughout this paper we show sky maps\
               in Galactic coordinates centered on the Galactic center and observed by the solar position.\
               The red arrow at the center of the\
               top panel depicts the direction of the bipolar jet, constantly ejecting at an angle of $45^{\circ}$\
               to the disk normal in 1.2 Myr.]
     {
      \includegraphics[width=0.8\linewidth]{figures/fig__xraymap.png}
      \label{fig__xray_0.8keV_angle_000}
     }
    \subfigure[Comparison of simulated (red) and observed (black; \citealt{Predehl2020}) one-dimensional\
               count rate profiles in the same energy band as \Cref{fig__xray_0.8keV_angle_000},\
               cut at various galactic latitudes (as labelled).]
     {
      \includegraphics[width=0.8\linewidth]{figures/fig__xray-profile-0.8keV-000.png}
      \label{fig__x-ray-profile-0.8keV-000}
     }
    \caption{}
    \label{fig_xray}
  \end{figure*}

>>>>

Early attempts \citep{Sarkar2015,Yang2017,Zhang2020}\
to model the symmetric Fermi and eROSITA bubbles (collectively we call the Galactic bubbles)\
assumed that the jet is vertical to the Galactic plane. However,\
observation \citep{Gallimore2006} has proposed that\
there is a lack of preferred orientation of jets with respect to a disc normal.\
A number of galaxies in which the jets are tilted to the disc normal\
(e.g. NGC 3079, \citealt{Cecil2001}; NGC 1052, \citealt{Dopita2015}),\
including galaxies in which the jets lie in the plane of the disc (e.g. IC 5063, \citealt{Morganti2015}).

To this end, this work introduces a dense thin disc of interstellar medium\
around a jet source to deflects and decelerates the jets,\
in an attempt to remedy the symmetry problem of the Galactic bubbles.\

@@

  Since the relativistic fluid ejected by the jet source\
  is quickly stalled off and slowed down by a dense ISM disc in a short time,\
  and the relativistic fluid\
  accounts for a little minority of total mass inside the simulation box,\
  we still use the Newtonian gravity to attack this problem.

@@

  With the help of the isothermal and hydrostatic equilibrium conditions,\
  and assuming the interfaces between isothermal disc and atmosphere are in thermal pressure equilibrium,\
  we can write the steady-state gaseous density distributions,\
  confined in the total potential, of the disc and the Galactic atmosphere as\
  \begin{subequations}
  \begin{align}
     \displaystyle \rho_{\text{isoDisk}}(z) = \rho_{\text{isoDisk}}^{\text{peak}}
     \exp\left[-\frac{\Phi_{\text{total}}(z)}{k_{B}T_{\text{isoDisk}}/m_{\text{p}}}\right]&\label{isothermal-disc-density}\\
     \text{, if $|z| < z_{0}$}& \nonumber \\
     \nonumber\\
     \displaystyle \rho_{\text{atmp}}(z) = \rho_{\text{atmp}}^{\text{peak}}
     \exp\left[-\frac{\Phi_{\text{total}}(z)}{k_{B}T_{\text{atmp}}/m_{\text{p}}}\right]&\label{isothermal-atmp-density}\\
     \text{, otherwise,}& \nonumber
  \end{align}
  \label{disc-atm-sys}
  \end{subequations}
  where $m_{\text{p}}$ is the proton mass,\
  $T_{\text{isoDisk}}$ and $T_{\text{atmp}}$ is the temperature of the isothermal disc and atmosphere,\
  $\rho_{\text{isoDisk}}^{\text{peak}}$ and $\rho_{\text{atmp}}^{\text{peak}}$ is the peak mass density\
  of the disc and atmosphere on the mid-plane $z=0$.

  We tabulate parameters in the first four\
  categories of \Cref{table-parameters},\
  except for $\rho_{\text{atmp}}^{\text{peak}}$ that\
  can be derived from the other known parameters and thermal pressure equilibrium condition\
  on the interfaces $(z=\pm z_{0})$ between the disc and atmosphere.\

  The density profile of \Cref{disc-atm-sys} is shown in \Cref{fig__initial-density-profile}.\
  Beyond the core radius ($\sim 2 \text{ kpc}$) the gaseous density decreases rapidly as a power-law.

%  The density profile of \Cref{disc-atm-sys} is shown in \Cref{fig__initial-density-profile}\
%  and compared to the observed result \citep{Miller_2013} beyond 1 kpc.\
%
%  Note that there is an difficulty in disentangling the contribution\
%  of the Local Bubble, a supernova remnant in which the Solar System is embedded \citep{Snowden1990},\
%  and the contribution from solar wind charge-exchange processes, which produce soft\
%  X-ray emission throughout the Solar System. As a result, the density profile of the Galactic halo remains unclear\
%  \citep{BlandHawthorn2016}.

  \begin{figure}
    \includegraphics[width=\columnwidth]{figures/fig__initial-density-profile.png}
    \caption{The density profile of the isothermal disc (red pluses) and\
             atmosphere (blue crosses) along the positive z-axis.\
             The density distribution is derived from hydrostatic equilibrium,\
             the interface ($z=0.1$) between the isothermal disc\
             and the atmosphere is pressure balanced.}
    \label{fig__initial-density-profile}
  \end{figure}

@@

  A crucial component in our work is the clumpy ISM disc initialized by\
  the publicly available pyFC code
  \footnote{\url{https://pypi.python.org/pypi/pyFC}}.\

  pyFC randomly generates dimensionless 3D scalar field $f(\bold{x})$\ % that is clumpy and porous.
  that obeys the log-normal probability distribution\
  with mean $\mu$ and dispersion $\sigma$,\
  and follows the power-law Kolmogorov spectrum
  \begin{equation}
    D(\bold{k})=\int k^{2} \hat{f}(\bold{k})\hat{f}^{*}(\bold{k})d\Omega \propto k^{-\beta},
    \label{Kolmogorov-spectrum}
  \end{equation}
  where $\hat{f}(\bold{k})$ is the Fourier transform of $f(\bold{x})$.\
  The spectrum $D(\bold{k})$ in the Fourier space is characterized by the power law index $\beta=5/3$,\
  the Nyquist limit $k_{\text{max}}$, and the lower cutoff wave number $k_{\text{min}}$.
  $k_{\text{max}}$ is one-half of the spatial resolution within disc,\
  and $k_{\text{min}}$ is 375.0, corresponding to the maximum size of an individual clump $\sim 20$ pc.\
  \citet{LA2002} and \citet{Wagner2012} have outlined a detailed procedure\
  for constructing a clumpy scalar field, and we do not repeat here.

  The density of clumpy disc can thus be obtained by taking the scalar products of\
  $f(\bold{x})$ with $\rho_{\text{isoDisk}}(z)$ over all cells within the disc, i.e.,\
  $\displaystyle\rho_{\text{ismDisk}}(\bold{x}) =\
  f(\bold{x}) \rho_{\text{isoDisk}}(z)$.\
  Also, the thermal pressure equilibrium within the clumpy disc implies that the temperature of disc is
  $\displaystyle T_{\text{ismDisk}}(\bold{x}) =\
  T_{\text{isoDisk}}(z)\rho_{\text{isoDisk}}(z)/\rho_{\text{ismDisk}}(\bold{x})$.

  \Cref{table-parameters} summarize the parameters of the clumpy disc and their references.

  On the basis of this setup, we cover the AMR base level with\
  $16\times16\times32$ root cells, refined progressively on the mid-plane $z=0$\
  based on the gradient of mass density.\
  We also restrict the refinement level at 7 within the cold disc so that\
  a molecular cloud can be adequately resolved by approximately 30 cells along their diameter, 20 pc.

  \Cref{fig__zoom-in-disc} shows a close-up view of the\
  pressure, temperature, and number density slices
  in the y-z plane through the center of the disc.

  \Cref{fig__numberDensityHistogram} plots the volume filling factor as a function of\
  initial number density within the disc without jet source.\

  \begin{figure}
      \includegraphics[width=\columnwidth]{figures/fig__numberDensityHistogram.png}
    \caption{The volume filling factor as a function of\
             initial number density within the disc without jet source.\
             The vertical bands represent from left to right: the allowable number densities \citep{peak-ism-density} for\
             hot ionized, warm neutral (WNM), warm ionized (WIM), cold nuetral mediums (CNM), and molecular clouds.}
      \label{fig__numberDensityHistogram}
  \end{figure}

  \begin{figure}
    \includegraphics[width=\columnwidth]{figures/fig__zoom-in-disc.png}
    \caption{Close-up view of the initial\
             pressure (top), temperature (middle), and number density (bottom) slices\
             in the y-z plane through the center of the disc.
             }
    \label{fig__zoom-in-disc}
  \end{figure}

\begin{table*}[t]
\raggedright
\caption{Parameters of the disc, atmosphere, and gravitational potential in the simulation.}
\label{table-parameters}
\begin{tabular}{@{}llrc@{}}
\toprule[1pt]\midrule[0.3pt]
Parameter                             & Description                               & Value                                &  Reference                     \\ \midrule
{\bf Static stellar potential }       &                                           &                                      &                                \\
$\sigma_{\text{bulge}}$               & Velocity dispersion of bulge              & 100 km$\cdot$s$^{-1}$                & \citep{velocity-dispersion-MW} \\
$\rho_{\text{bulge}}^{\text{peak}}$   & Peak average density of bulge             & $4\times 10^{-24}$ g$\cdot$cm$^{-3}$ &   N/A                          \\ \hline
{\bf Static dark halo potential }     &                                           &                                      &                                \\
$v_{\text{halo}}$                     &                                           & 131.5 km$\cdot$s$^{-1}$              & \citep{Johnston1995}           \\
$d_{\text{h}}$                        & Core radius                               & 12 kpc                               & \multicolumn{1}{c}{''}         \\ \hline
{\bf Atmosphere }                     &                                           &                                      &                                \\
$T_{\text{\text{atmp}}}$              & Temperature of atmosphere                 & $10^{6}$ K                           & \citep{temperature-MW}         \\ \hline
{\bf Isothermal disc }                &                                           &                                      &                                \\
$z_{0}$                               & Scale height of disc                      & 100 pc                               & \citep{peak-ism-density}       \\
$T_{\text{\text{isoDisk}}}$           & Temperature of disc                       & $10^{3}$ K                           & \multicolumn{1}{c}{''}         \\
$\rho_{\text{isoDisk}}^{\text{peak}}$ & Peak mass density of disc                 & $10^{-23}$ g$\cdot$cm$^{-3}$         & \multicolumn{1}{c}{''}         \\ \hline
{\bf Clumpy disc }                    &                                           &                                      &                                \\
$\dagger$  $k_{\text{min}}$           & Cutoff wave number                        & 375.0                                & \citep{peak-ism-density}       \\
$\mu$                                 & Mean of scalar field                      & 1.0                                  &   N/A                          \\
$\ddag$  $\sigma$                     & Dispersion of scalar field                & 5.0                                  & \citep{Federrath2010}          \\
$\beta$                               & Power law index                           & -5/3                                 &   N/A                          \\ \midrule
\end{tabular}
\begin{tablenotes}
      \raggedright
      \item  $\dagger$  $k_{\text{min}}=375.0$ leads to the size of an individual molecular cloud $\sim 100$ pc.
      \item  $\ddag$ In numerical simulations of turbulence,\
             \citet{Federrath2010} find $\sigma\sim 3.6$ and 35 for solenoidal (divergence-free)\
             and compressive (curl-free) driving force,\
             respectively, so that our adopted value of 5 is closer to their solenoidal result.
    \end{tablenotes}
\end{table*}

% In addition to the gravitational interaction, we ignore other interactions between stars and gases.
% We also ignore the self-gravity of the ISM disc and of the atmosphere.
% We ignore the centrifugal force of Milky Way rotation acting on the bubbles.
%

@@

  Motivated by these observations, we simulate the jet with an inclination angle\
  $45^{\circ}$ with respect to the Galactic plane\
  in order to release the caveat that\
  the jet direction must be perpendicular to the Galactic plane, and in particular to\
  investigate the effect of the jet-disc misalignment on the symmetry of bubbles.

@@

  Note that as we inject the jets at the center of the clumpy disc,\
  we define the ambient gas density by the peak density of\
  the isothermal disc on the mid-plane $z=0$ (i.e. $\rho^{\text{peak}}_{\text{isoDisk}}$),\
  as opposed to the \textit{clumpy} density around the jet source, to avoid ambiguous definition.

@@

\section{Results}
\label{Results}
  \begin{figure}
    \includegraphics[width=\columnwidth]{figures/fig__jetI5+ismSeed3-45deg_no-disc-stratified-ambient-Pres-Dens-Temp.png}
    \caption{
             The pressure (top), temperature (middle), and number density (bottom) slices\
             through a bipolar jet sources injecting along $z=-y$ direction from\
             the origin for a duration of 1.2 Myr under four different cases from left to right.\
             Comparison between the cases with a clumpy (first column from left)\
             and with a smooth disc (second) in a stratified atmosphere\
             shows that the initial density distribution of the dense disc has an insignificant effect\
             on the overall dynamics of bubbles. However, the outer bubbles with the smooth disc\
             in an uniform atmosphere (third) is spherical-shape,\
             suggesting the stratification facilitates the outer bubbles elongation significantly.\
             Also, the first three and the rightmost columns show that the most inner bubbles (dashed box)\
             can only appear associated with the disc, and without the disc, the outer bubbles will be tilted,
             indicating the dense disc is crucial for\
             the axis-symmetrically outer bubbles and of the most inner bubbles formation.
             }
    \label{fig__jetI5+ismSeed3-45deg_no-disc-stratified-ambient-Pres-Dens-Temp}
  \end{figure}

@@

  \begin{figure*}
    \subfigure[Simulated (top) and observed (bottom; \citealt{Predehl2020}) count rate\
               (photons s$^{-1}$ deg$^{-2}$) in the 0.6-1.0 keV range,\
               using a Hammer-Aitoff projection. Throughout this paper we show sky maps\
               in Galactic coordinates centered on the Galactic center and observed by the solar position.\
               The red arrow at the center of the\
               top panel depicts the direction of the bipolar jet, constantly ejecting at an angle of $45^{\circ}$\
               to the disc normal in 1.2 Myr.]
     {
      \includegraphics[width=0.8\linewidth]{figures/fig__xraymap.png}
      \label{fig__xray_0.8keV_angle_000}
     }
    \subfigure[Comparison of simulated (red) and observed (black; \citealt{Predehl2020}) one-dimensional\
               count rate profiles in the same energy band as \Cref{fig__xray_0.8keV_angle_000},\
               cut at various galactic latitudes (as labelled).]
     {
      \includegraphics[width=0.8\linewidth]{figures/fig__xray-profile-0.8keV-000.png}
      \label{fig__x-ray-profile-0.8keV-000}
     }
    \caption{}
    \label{fig_xray}
  \end{figure*}
